Uncertainty-aware graph-based multimodal remote sensing classification

### 2021-07-02 latex/CEUR/paper.tex
Added 28421 around numbers in table

\begin{table*}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by AUROC and AUPR).}
\label{tab::misc_auroc}
\small
\begin{center}
\begin{tabular}{Y|ccccc|ccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}\vline&\multicolumn{5}{c}{AUPR}        \\
                        & Vac. & Dis. & Ale. & Epi. & Ent. & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) & $0.676$ & $0.801$ &$0.792$&$0.509$&$0.798$&0.352&0.398&0.467&0.237&0.474    \\
S-BGCN-T-K (pixel prior) & $0.908$ & $0.840$ &$0.905$&$0.451$&$\mathbf{0.912}$&0.659&0.545&0.649&0.206&0.672  \\
S-BGCN-T & $0.729$ & $0.834$ &$0.869$&$0.618$&$0.861$&0.451&0.484&0.591&0.278&0.579  \\ 
S-BGCN & $0.760$ & $0.877$ &$0.894$&$0.623$&$0.886$&0.489&0.558&0.633&0.268&0.616  \\ 
S-GCN & $0.729$ & $0.842$ &-&-&$0.859$&0.472&0.538&-&-&0.595  \\ 
S-MLP &$0.845$&$0.904$&-&-&$0.909$&0.417&0.566&-&-&0.606  \\
GCN & - & - &-&-&$0.887$&-&-&-&-&0.606  \\ 
Drop-GCN & - & - &$0.897$&$0.552$&$0.887$&-&-&0.619&0.243&0.600  \\ \hline
\end{tabular}
\end{center}
\end{table*}

>>>>

\begin{table*}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by AUROC and AUPR).}
\label{tab::misc_auroc}
\small
\begin{center}
\begin{tabular}{Y|ccccc|ccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}\vline&\multicolumn{5}{c}{AUPR}        \\
                        & Vac. & Dis. & Ale. & Epi. & Ent. & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) & $0.676$ & $0.801$ &$0.792$&$0.509$&$0.798$&$0.352$&$0.398$&$0.467$&$0.237$&$0.474$    \\
S-BGCN-T-K (pixel prior) & $0.908$ & $0.840$ &$0.905$&$0.451$&$\mathbf{0.912}$&$0.659$&$0.545$&$0.649$&$0.206$&$\mathbf{0.672}$  \\
S-BGCN-T & $0.729$ & $0.834$ &$0.869$&$0.618$&$0.861$&$0.451$&$0.484$&$0.591$&$0.278$&$0.579$  \\ 
S-BGCN & $0.760$ & $0.877$ &$0.894$&$0.623$&$0.886$&$0.489$&$0.558$&$0.633$&$0.268$&$0.616$  \\ 
S-GCN & $0.729$ & $0.842$ &-&-&$0.859$&$0.472$&$0.538$&-&-&$0.595$  \\ 
S-MLP &$0.845$&$0.904$&-&-&$0.909$&$0.417$&$0.566$&-&-&$0.606$  \\
GCN & - & - &-&-&$0.887$&-&-&-&-&$0.606$  \\ 
Drop-GCN & - & - &$0.897$&$0.552$&$0.887$&-&-&$0.619$&$0.243$&$0.600$  \\ \hline
\end{tabular}
\end{center}
\end{table*}
